### 2019-02-02 results.tex
rich makes a pass at the results section

\begin{table}[t]
\centering
\scriptsize
\resizebox{\columnwidth}{!}{
\begin{tabular}{|l|l|} \hline
\textbf{Application}& \textbf{Description}\\
\hline
Prophet& Time series decomposition and prediction\\ 
\hline
Multi-Regression& Multiple linear regression/prediction of time series\\
\hline
XGBoost& Regression and classification by gradient boosting\\
\hline
SVC & Classification based on support vector machine\\
\hline
Neural Network& Classification by layered artificial neural network\\
\hline
\end{tabular}}
\caption{Machine learning applications used as benchmarks
to evaluate Seneca. 
%paper submission is blind (so such references must be omitted so as not to reveal our identities):
%Code base is available at project repository~\cite{ref:seneca}.
\label{tab:bmarks}}
\vspace{-0.2in}
\end{table}

@@

\begin{table}[t]
\centering
\scriptsize
\resizebox{\columnwidth}{!}{
\begin{tabular}{|l|l|l|} 
\hline
\textbf{Hyperparameter}& \textbf{Default} & \textbf{Tuning options}\\
\hline
grow & linear & [linear, logistic] \\
\hline
changepoint prior scale & 0.05 & [0.05, 0.5] \\
\hline
holidays prior scale & 10 & [1, 5, 10] \\
\hline
seasonality prior scale & 0.5 & [0.1, 0.5] \\
\hline
fourier order & 10 & [5, 10, 15, 20] \\
\hline
seasonality mode & additive & [additive, multiplicative] \\
\hline
interval width & 0.8 & [0.5, 0.8] \\
\hline
\end{tabular}}
\caption{The selected configurable hyperparameters of Prophet. The default value and tuning options are listed. 
\label{tab:prophet_para}}
\vspace{-0.2in}
\end{table}

@@

A hyperparameter configuration for this application is a subset of input SBC time series.
Seneca considers all \texttt{$2^N - 1$} potential subsets (for $N$ input time series).
For this application,
we assume the default parameterization is the set of all $N$ input time series (8 in this case).
The test dataset for this application is a time series of the outdoor temperature (ground truth) 
over the same period.  The application makes predictions for each of these outdoor temperatures
using the model constructed from the training set
and computes the mean square error across predicted and ground truth value pairs.

@@

For these applications (XGBoost, SVC, and Neural Network), 
we use a labeled dataset for training, testing, and evaluation from 
this project~\cite{iot-cpu}. The dataset contains
measurements from individual citrus fruit (e.g. oranges, mandarins, lemons, etc.) 
taken by a fruit sorting and grading device (using a large number of sensors).  
The measurements (i.e. features)
include size, shape, weight, color, diameter, flatness, among other characteristics,
for each fruit.  The label indicates which field the fruit was harvested from.  
The applications train a model on a random subset of the data.  
They then use this model to predict the field
%%<<<<<<< HEAD
%%from which each fruit originates.  They compute classification accuracy 
%%as \textcolor{blue}{finish this.}.  XGBoost also computes MSE for its regression task
%%on the same datasets.  The dataset has been filtered authors to remove correlated 
%%features (those with an absolute value of the Pearson correlation coefficient greater than 0.8).  
%%The resulting dataset contains 218150 rows (individual fruit) each with 19 features. 
from which each fruit originates. They compute classification accuracy score as $\frac{1}{n}\sum_{i=1}^{n}1(Y_i = \hat{Y_i})$, where $Y_i$ is the prediction class, $Y_i$ is the true class, n is the number of samples and 1(x) is the indicator function. XGBoost also computes MSE for its regression task on the same datasets. The dataset has been filtered to remove correlated features (those with an absolute value of the Pearson correlation coefficient greater than 0.8). The dataset has also been balanced by downsampling one target whose number greatly exceeds other ones. The resulting dataset contains 33926 rows (individual fruit) distributed evenly to 5 targets and each row has 18 features.

@@

%Seneca downloads the dataset from AWS S3 for each function invocation.
%It then randomly indexes the data set and splits it into two.  
For these applications (XGBoost, SVC, and Neural Network), we consider three split scenarios for training and testing: 80\%-20\%, 20\%-80\% and 0.1\%-99.9\%. As the proportion of training data decreases, the performance of classifier degrades accordingly and we argue that Seneca is able to eke out improvement even with very limited training data.
%\textcolor{blue}{list them here once we finish the additional results} 
%This setup also means that each Seneca function
%considers a different training and testing set during hyperparameter tuning.

@@

\subsection{Empirical Methodology}
To evaluate Seneca, we measure tuning performance, application execution time, and monetary cost.
For tuning performance, we use mean squared error (MSE) for regression tasks 
and percentage accuracy for
classification tasks. The default configuration that we 
consider for each application is described above.
We report results for the default, best (Seneca's recommendation), 
and worst performing configurations.  Seneca computes all possible combinations 
of the hyperparameter settings specified in the configuration to extract each of these results.
The default results represents those that a novice or first time 
user might employ when using these applications
as a "black box".  The worst performing scenario shows how bad the results can be
when parameters are poorly tuned.  Finally, the best is the upper bound on what is possible from 
tuning the hyperparameters (e.g. using expert knowledge or Seneca).

We deploy Seneca on Amazon Web Services (AWS) Lambda and extract
execution time and memory use from AWS CloudWatch logs.  We then compute monetary cost
using the AWS Lambda pricing model~\cite{ref:pricing}.
%awslambdapricing: https://aws.amazon.com/lambda/pricing/
Each function downloads the training and testing dataset 
of the application from AWS Simple Storage Service (S3) upon function invocation. 
We do not consider the cost of dataset storage in our cost computations (it is very small).

We also experiment with different memory configurations for Seneca functions in AWS Lambda.  
We evaluate
the performance and cost of allocating the maximum memory for each and for automatically optimizing 
memory use using Seneca. We assume that all combinations hyperparameter settings use the 
same maximum amount of memory across functions; we 
have verified that this assumption holds for the applications and datasets we consider.
We plan to consider applications for which hyperparameter settings require 
different maximum amounts of memory as part of future work.

\subsection{Tuning Performance}

@@

\begin{figure}[t] \centering 
\includegraphics[scale=0.36]{box_plot_mse_2}
\caption{The box plot of MSE metric from three regression applications in the entire hyperparameter tuning search space. The red notch shows the MSE from the default settings. The colored diamonds are outliers beyond two interquartile ranges. Lower MSE values are better.
\label{fig:box_plot_mse}}
\vspace{-0.2in}
\end{figure}

We first evaluate Seneca using the three regression applications: 
Prophet, Multi-Regression, and XGBoost (regression task). 
Table ~\ref{tab:mse} shows the size of the hyperparameter search space (number of configurations
considered) and the mean squared error (MSE)
for each of the regression applications that we consider (columns 3-5).
The first row of data is 
 the number of hyperparameter configurations in the search space of each. 
The last three rows show the MSE for the default, worst, and best performing 
hyperparameter configuation reported by Seneca (lower is better).  
Note that Seneca's recommendation is the best performing configuration.
Seneca reduces MSE by 26\%, 16\%, and 63\%, for Prophet, Multi-Regression, and XGBoost,
respectively, for the datasets and training methodologies that we consider.
Verses the worst case, Seneca reduces MSE by 83\%, 78\%, and 99\%, respectively.

Figure~\ref{fig:box_plot_mse} provides a box plot of MSE (lower is better)
for these applications 
for the entire hyperparameter 
search space. The central rectangle covers the interquartile range (IQR), 
which is defined as the range of data 
points from first quartile to third quartile (Q3 - Q1). 
The upper whisker extends to the last datum less 
than \texttt{$(Q3 + 2 * IQR)$} and the lower whisker extends to the first datum greater 
than \texttt{$(Q1 - 2 * IQR)$}. The data points beyond the whiskers are considered outliers 
and are plotted as colored diamonds. The red notch identifies the MSE that results from training 
the model using the default settings of hyperparameter. The difference between red notch of lowest data 
point is improvement brought about through the use of Seneca. From the location of red notch, we can see the MSE metrics from default configuration in three applications are close to the first quartile value, meaning the potential room for improvement is about 75\% over the range of MSE metric. The box plot also illustrates that the best MSE of Prophet and multivariate regression are among outliers, where a comprehensive search is very critical to find the best configurations. 
%\textcolor{blue}{Add more analysis here to discuss the variance in the MSE for the range of configurations and how they change across applications. Include any insights that the boxplots add.}

%%%%%%%%%%%%%%%%%%%%% classification apps - tuning performance %%%%%%%%%%%%%%%%%%%%%%%%%
We next empirically evaluate the tuning performance of Seneca for the three
classification applications: XGBoost (classification), SVC, and Neural Network.
Table~\ref{tab:accuracy} presents the accuracy percentage (higher is better) 
reported by each application (3 right-most columns) 
for the default, worst, and best hyperparameter tuning configurations under three training and testing split scenarios reported by Seneca.  
In the 80/20 percent split case, Seneca increases accuracy by 3.43\%, 62.52\%, and 0.53\%, for XGBoost (classification), 
SVC, and Neural Network applications,
respectively.
Verses the worst case, Seneca improves accuracy by 99.13\%, 75.75\%, and 65.57\%, respectively.

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{80\%-20\%} & XGBoost & SVC & Neural Network\\
\hline
\hline
Default Accuracy & 95.70\% & 21.77\% & 84.23\%\\
\hline
Worst Accuracy&0.00\%&7.53\% & 19.19\%\\
\hline
Best Accuracy (Seneca) &99.13\% & 83.29\% & 84.76\%\\
\hline
\hline
\textbf{20\%-80\%} & XGBoost & SVC & Neural Network\\
\hline
Default Accuracy & 95.07\% & 21.31\% & 55.44\%\\
\hline
Worst Accuracy&0.00\% & 9.42\% & 19.55\%\\
\hline
Best Accuracy (Seneca) & 98.68\% & 43.61\% & 60.89\%\\
\hline
\hline
\textbf{0.1\%-99.9\%} & XGBoost & SVC & Neural Network\\
\hline
Default Accuracy & 86.37\% & 20.02\% & 20.00\%\\
\hline
Worst Accuracy & 0.00\% & 19.99\% & 19.79\%\\
\hline
Best Accuracy (Seneca) & 89.14\% & 55.79\% & 29.99\%\\
\hline

%percent difference between default and best 83.65%, 83.84%, 79.83%
%percent difference between worst and best 86.07%, 85.73%, 84.63%
%\begin{figure}[t] \centering 
%\includegraphics[scale=0.38]{accuracy}
\end{tabular}
\caption{The Accuracy reported for the 
default, best (Seneca's recommendation), and worst hyperparameter configurations for 
the three classification applications under three train/test split scenarios.  
For the accuracy values in the table, higher is better.
\label{tab:accuracy}}
%\vspace{-0.2in}
%\end{figure}
\end{table}

@@

Figure~\ref{fig:box_plot_accuracy} presents the accuracy (higher is better) 
for the entire hyperparameter search space for each classification
application.  The central rectangle covers from first quartile to third quartile (Q3 - Q1) and the whiskers span from \texttt{$(Q3 + 2 * IQR)$} to \texttt{$(Q1 - 2 * IQR)$}. The red notch indicates the accuracy metric from the model trained by default settings and colored diamonds are outliers beyond whiskers.
For both types of applications (regression and classification), Seneca significantly
improves tuning performance over the default and worst case configurations for the 
datasets and training methodologies we consider.

@@

We next analyze the monetary cost introduced by Seneca. 
We consider two scenarios for its implementation.
First, we configure each lambda function to use the maximum amount
of memory allowed by AWS Lambda (3008 MB).  Second, we employ Seneca's memory optimization 
which automatically detects and configures the amount of memory needed by each function.
Because memory impacts both cost and execution time (total latency of Seneca hyperparameter tuning), 
we present empirically evaluate both 
in this subsection.  For each, we only include XGBoost once since its 
performance profile is the same
regardless of whether we are using regression or classification.

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|c|c|}
\hline
& Prophet & MR & XGBoost & SVC & NN\\
\hline
\hline
Exec time (minutes)& 24.96 & 4.18 & 17.48 & 0.91 & 2.49 \\
\hline
Cost of Tuning (\$) & 0.722 & 0.121 & 0.5 & 0.023 & 0.072 \\
\hline
\end{tabular}
\caption{ Monetary cost of using Seneca for hyperparameter tuning when configured to use the maximum amount of memory (3008 MB) possible for each function invocation. 
\label{tab:cost_max_memory}}
\vspace{-0.2in}
\end{table}

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|c|c|}
\hline
& Prophet & MR & XGBoost & SVC & NN\\
\hline
\hline
Exec time (minutes)& 38.7 & 8.72 & 29.07 & 0.91 & 3.17 \\
\hline
Cost of Tuning (\$) &0.62 & 0.086 & 0.354 & 0.007 & 0.056 \\
\hline
Cost of optimization (\$) &0.033 & 0.014 & 0.003 & 0.010 & 0.008 \\
\hline
Total Cost (\$) &0.653 & 0.1 & 0.357 & 0.016 & 0.064 \\
\hline
\end{tabular}
\caption{ Seneca  Memory  Optimization:  The  monetary  cost  of using Seneca for hyperparameter tuning when the amount of memory  used  for  each  function  invocation  is  automatically inferred and set by Seneca.
\label{tab:cost_optimized}}
\vspace{-0.2in}
\end{table}

Tables~\ref{tab:cost_max_memory} and~\ref{tab:cost_optimized} show the results with and without 
the Seneca memory optimization, respectively. In both tables, the five columns identify the 
benchmark applications and the first row is the total execution time in minutes for 
Seneca's hyperparameter tuning for the corresponding application.  
In table~\ref{tab:cost_max_memory}, the second row is total cost of tuning when Seneca's 
lambda functions are configured to use the maximum amount of memory (3008 MB), whereas table~\ref{tab:cost_optimized} demonstrates the additional cost of optimization in the third row 
and total cost on fourth row.
% \textcolor{blue}{See my notes to fix the tables in the caption of these figures.}

@@

% \textcolor{red}{state what the columns and rows are; then write up some analysis on what the table data is showing and why. provide analysis for both tables and summarize the key differences between them.}

%The results of maximum memory scenario are shown in Figure~\ref{fig:cost_max_memory}. The max memory used and billed duration are reported by AWS CloudWatch and averaged throughout whole search space for each application. Figure ~\ref{fig:cost_optimized} demonstrates the results of optimized memory scenario. The total cost stems from function optimization and hyperparameter tuning. As a comparison of two scenarios, Figure~\ref{fig:cost_analysis} illustrates the total cost of optimized memory scenario is lower than maximum memory scenario in each application respectively.

\begin{figure}[t] \centering 
\includegraphics[scale=0.36]{Cost_analysis_2}
\caption{ The cost analysis of Seneca with (Opt) and without (No Opt) the use of its memory optimization. 
By reducing the memory use of each, Seneca reduces the monetary cost of hyperparameter tuning by \textcolor{blue}{X\% on average, across these applications.  *compute and Fill this X in*.}
\textcolor{blue}{Change the legend as follows: change "Tuning at Max Memory" to "No Opt"; change "Function Optimization" to "Opt cost"; change "Tuning" to "Opt". If you can put legend in this order: Opt, Opt cost, No Opt} 
\label{fig:cost_analysis}}
\vspace{-0.2in}
\end{figure}

>>>>

\begin{table}[t]
\centering
\scriptsize
\resizebox{\columnwidth}{!}{
\begin{tabular}{|l|l|} \hline
\textbf{Application}& \textbf{Description}\\
\hline
Prophet& Time series decomposition and prediction\\ 
\hline
Multi-Regression& Multiple linear regression/prediction of time series\\
\hline
XGBoost& Regression and classification by gradient boosting\\
\hline
SVC & Classification based on support vector machine\\
\hline
Neural Network& Classification by layered artificial neural network\\
\hline
\end{tabular}}
\caption{Machine learning applications used as benchmarks
to evaluate Seneca. 
%paper submission is blind (so such references must be omitted so as not to reveal our identities):
%Code base is available at project repository~\cite{ref:seneca}.
\label{tab:bmarks}}
%\vspace{-0.2in}
\end{table}

@@

\begin{table}[t]
\centering
\scriptsize
\resizebox{\columnwidth}{!}{
\begin{tabular}{|l|l|l|} 
\hline
\textbf{Hyperparameter}& \textbf{Default} & \textbf{Tuning options}\\
\hline
grow & linear & [linear, logistic] \\
\hline
changepoint prior scale & 0.05 & [0.05, 0.5] \\
\hline
holidays prior scale & 10 & [1, 5, 10] \\
\hline
seasonality prior scale & 0.5 & [0.1, 0.5] \\
\hline
fourier order & 10 & [5, 10, 15, 20] \\
\hline
seasonality mode & additive & [additive, multiplicative] \\
\hline
interval width & 0.8 & [0.5, 0.8] \\
\hline
\end{tabular}}
\caption{The selected configurable hyperparameters of Prophet. The default value and tuning options are listed. 
\label{tab:prophet_para}}
%\vspace{-0.2in}
\end{table}

@@

A hyperparameter configuration for this application is a subset of input SBC time series.
Seneca considers all \texttt{$2^N - 1$} potential subsets (for $N$ input time series).
For this application,
we assume the default parameterization is the set of all $N$ input time series (8 in this case).
The test dataset for this application is a time series of the outdoor temperature (ground truth) 
over the same period.  The application makes predictions for each of these outdoor temperatures
using the regression coefficients constructed from the training set
and computes the mean square error between predicted and ground truth value pairs.

@@

For these applications (XGBoost, SVC, and Neural Network), we use a labeled
dataset for training, testing, and evaluation from this
project~\cite{iot-cpu}. The dataset contains measurements from individual
citrus fruit (e.g. oranges, mandarins, lemons, etc.) taken by a fruit sorting
and grading device (using a large number of sensors).  The measurements (i.e.
features) include size, shape, weight, color, diameter, flatness, among other
characteristics, for each fruit.  The label indicates which field the fruit
was harvested from.  The applications train a model on a random subset of the
data.  They then use this model to predict the field
%%<<<<<<< HEAD %from which each fruit originates.  They compute classification
%accuracy %as \textcolor{blue}{finish this.}.  XGBoost also computes MSE for
%its regression task %on the same datasets.  The dataset has been filtered
%authors to remove correlated %features (those with an absolute value of the
%Pearson correlation coefficient greater than 0.8).  %The resulting dataset
%contains 218150 rows (individual fruit) each with 19 features. 
from which each fruit originates. They compute classification accuracy score
as $\frac{1}{n}\sum_{i=1}^{n}1(Y_i = \hat{Y_i})$, where $Y_i$ is the
prediction class, $Y_i$ is the true class, n is the number of samples and 1(x)
is the indicator function. XGBoost also computes MSE for its regression task
on the same datasets. The dataset has been filtered to remove correlated
features (those with an absolute value of the Pearson correlation coefficient
greater than 0.8). The dataset has also been balanced by downsampling one
target whose number greatly exceeds other ones. The resulting dataset contains
33926 rows (individual fruit) distributed evenly to 5 targets and each row has
18 features.

@@

%Seneca downloads the dataset from AWS S3 for each function invocation.
%It then randomly indexes the data set and splits it into two.

For these applications (XGBoost, SVC, and Neural Network), we consider three
split scenarios for training and testing: 80\%-20\%, 20\%-80\% and
0.1\%-99.9\%. As the proportion of training data decreases, the performance of
classifier degrades accordingly.  However we note that using the optimized
hyperparameters generated by Seneca, these calssifiers are able to achieve
accuracy levels similar to those generated from the default parameters, but
with significantly less training data.

% and we argue that Seneca is able to eke out
%improvement even with very limited training data.

%\textcolor{blue}{list them here once we finish the additional results} 
%This setup also means that each Seneca function
%considers a different training and testing set during hyperparameter tuning.

@@

\subsection{Empirical Methodology}

To evaluate Seneca, we measure tuning performance, application execution time,
and monetary cost.  For tuning performance, we use mean squared error (MSE)
for regression tasks and percentage accuracy for classification tasks. The
default configuration that we consider for each application is described
above.  We report results for the default, best (Seneca's recommendation), and
worst performing configurations.  Seneca computes all possible combinations of
the hyperparameter settings specified in the configuration to extract each of
these results.  The default results represents those that a novice or first
time user might employ when using these applications as a ``black box.''  The
worst performing scenario shows how bad the results can be when parameters are
poorly tuned.  Finally, the best is the upper bound on what is possible from
tuning the hyperparameters (e.g. using expert knowledge or Seneca).

To evaluate the cost savings introduced by Seneca,
it on Amazon Web Services (AWS) Lambda~\cite{XXXaws-lambdaXXX} and extract
execution time and memory use from AWS CloudWatch~\cite{XXXcloudwatchCXXX} logs.  
We then compute monetary cost
using the AWS Lambda pricing model~\cite{ref:pricing}.
%awslambdapricing: https://aws.amazon.com/lambda/pricing/
Each function downloads the training and testing dataset 
of the application from AWS Simple Storage Service (S3) upon function invocation. 
We do not consider the cost of dataset storage in our cost computations (it is very small).

%We also experiment with different memory configurations for Seneca functions
%in AWS Lambda.  
We also investigate Seneca's automatic memory optimization capabilities.  To
do so we compare the execution performance and cost of the benchmarks using
the maximum allocatable memory size to the performance and cost when run with
Seneca's automatically determined memory size.  Note that this comparison
assume that the memory size used by each benchmark does not depend on
hyperparameter settings.  We have verified that this assumption holds for the
benchmarks and datasets we consider and plan to consider applications for
which hyperparameter settings require different maximum amounts of memory as
part of future work.

\subsection{Application Efficacy}

We begin by evaluating Seneca's effect on application efficacy.
That is, we detail the effect on the quality of the output generated by each
application when Seneca determines the hyperparameter settings.

@@

\begin{figure}[t] \centering 
\includegraphics[scale=0.36]{box_plot_mse_2}
\caption{The box plot of MSE metric from three regression applications in the entire hyperparameter tuning search space. The red notch shows the MSE from the default settings. The colored diamonds are outliers beyond two interquartile ranges. Lower MSE values are better.
\label{fig:box_plot_mse}}
%\vspace{-0.2in}
\end{figure}

%using the three regression applications: 
%Prophet, Multi-Regression, and XGBoost (regression task). 
Table~\ref{tab:mse} shows the effect of Seneca on the quality of the
regressions generated by Prophet, Multi-regression, and XGBoost (when used as
a regression algorithm). The first row of the table indicates the number of
different hyperparameter settings Senica considered.  Rows 3 through 5 show
the MSE generated by the default hytperparameter settings, the best (lowest
MSE) Seneca was able to find, and the worst (largest MSE) that Seneca tested
for each regression algorithm and data set.

%s mentioned previously, the table shows regression
%quality in terms of MSE. 
%
%size of the hyperparameter search space (number of configurations
%considered) and the mean squared error (MSE)
%for each of the regression applications that we consider (columns 3-5).
%The first row of data is 
% the number of hyperparameter configurations in the search space of each. 
%The last three rows show the MSE for the default, worst, and best performing 
%hyperparameter configuation reported by Seneca (lower is better).

%Note that Seneca's recommendation is the best performing configuration.
Compared to the default hyperparameter settings,
Seneca reduces MSE by 26\%, 16\%, and 63\%, for Prophet, Multi-Regression, and XGBoost,
respectively, for the datasets and training methodologies that we consider.
Verses the worst case, Seneca reduces MSE by 83\%, 78\%, and 99\%, respectively.

Figure~\ref{fig:box_plot_mse} provides a box plot of MSE (lower is better) for
these applications for the entire hyperparameter search space. The central
rectangle covers the interquartile range (IQR), which is defined as the range
of data points from first quartile to third quartile (Q3 - Q1).  The upper
whisker extends to the last datum less than \texttt{$(Q3 + 2 * IQR)$} and the
lower whisker extends to the first datum greater than \texttt{$(Q1 - 2 *
IQR)$}. The data points beyond the whiskers are considered outliers and are
plotted as colored diamonds. The red notch identifies the MSE that results
from training the model using the default settings of hyperparameter. The
difference between red notch of lowest data point is improvement brought about
through the use of Seneca. From the location of red notch, we can see the MSE
metrics from default configuration in three applications are close to the
first quartile value in all three cases (slightly greater that Q1 for Prophet
and Multi-regression and slight less for XGBoost).  However Seneca's MSE
performance is congruent with the end of the lower whisker.  Overall, however,
the quality of the application's output (for a given data set) is dramatically
affected by hyperparameter settings.  Perdictably the default settings are
near the ``good'' end of the spectrum, but as both Table~\ref{tab:mse} and
Figure~\ref{fig:box_plot_mse} indicate, Seneca is able to find
parameterization that improves output quality over the default settings
in each case.
%Thus for Prophet
%and Multi-Regression, Seneca 
%, meaning the potential room for improvement is about 75\%
%over the range of MSE metric. The box plot also illustrates that the best MSE
%of Prophet and multivariate regression are among outliers, where a
%comprehensive search is very critical to find the best configurations. 
%\textcolor{blue}{Add more analysis here to discuss the variance in the MSE
%for the range of configurations and how they change across applications.
%Include any insights that the boxplots add.}

%%%%%%%%%%%%%%%%%%%%% classification apps - tuning performance
%%%%%%%%%%%%%%%%%%%%%%%%%%
We next empirically evaluate the tuning performance of Seneca for the three
classification applications: XGBoost (classification), SVC, and Neural
Network.  Table~\ref{tab:accuracy} presents the accuracy percentage (higher is
better) reported by each application (3 right-most columns) for the default,
worst, and best hyperparameter tuning configurations under three training and
testing split scenarios reported by Seneca.  In the 80/20 percent split case,
Seneca increases accuracy by 3.43\%, 62.52\%, and 0.53\%, for XGBoost
(classification), SVC, and Neural Network applications, respectively.  Verses
the worst case, Seneca improves accuracy by 99.13\%, 75.75\%, and 65.57\%,
respectively.

\begin{table}
\centering
\begin{tabular}{|l|c|c|c|}
\hline
\textbf{80\%-20\%} & XGBoost & SVC & Neural Network\\
\hline
\hline
Default Accuracy & 95.70\% & 21.77\% & 84.23\%\\
\hline
Worst Accuracy&0.00\%&7.53\% & 19.19\%\\
\hline
Best Accuracy (Seneca) &99.13\% & 83.29\% & 84.76\%\\
\hline
%\hline
%\hline
%\textbf{20\%-80\%} & XGBoost & SVC & Neural Network\\
%\hline
%Default Accuracy & 95.07\% & 21.31\% & 55.44\%\\
%\hline
%Worst Accuracy&0.00\% & 9.42\% & 19.55\%\\
%\hline
%Best Accuracy (Seneca) & 98.68\% & 43.61\% & 60.89\%\\
%\hline
%\hline
%\textbf{0.1\%-99.9\%} & XGBoost & SVC & Neural Network\\
%\hline
%Default Accuracy & 86.37\% & 20.02\% & 20.00\%\\
%\hline
%Worst Accuracy & 0.00\% & 19.99\% & 19.79\%\\
%\hline
%Best Accuracy (Seneca) & 89.14\% & 55.79\% & 29.99\%\\
%\hline

%percent difference between default and best 83.65%, 83.84%, 79.83%
%percent difference between worst and best 86.07%, 85.73%, 84.63%
%\begin{figure}[t] \centering 
%\includegraphics[scale=0.38]{accuracy}
\end{tabular}
\caption{The Accuracy reported for the 
default, best (Seneca's recommendation), and worst hyperparameter configurations for 
the three classification applications using 80\% of the data to train and 20\%
of the data as a test set. 
%under three train/test split scenarios.  
For the accuracy values in the table, higher is better.
\label{tab:accuracy}}
%\vspace{-0.2in}
%\end{figure}
\end{table}

@@

The 80-20 case represents the typical usage of these classification
applications.  Often, when evaluating the accuracy of a specific classifier,
the user uses the 80-20 split ``rule'' when measuring accuracy.  In this case,
Seneca's improvement over the default parameterizations varies from less than
1\% for the Neural Network application (column 4 for 80-20), to 61.5\% for SVC
(best versus default in column 3 for 80-20 in the table).

Figure~\ref{fig:box_plot_accuracy} presents the accuracy (higher is better) 
for the entire hyperparameter search space for each classification
application.  The central rectangle covers from first quartile to third quartile (Q3 - Q1) and the whiskers span from \texttt{$(Q3 + 2 * IQR)$} to \texttt{$(Q1 - 2 * IQR)$}. The red notch indicates the accuracy metric from the model trained by default settings and colored diamonds are outliers beyond whiskers.
For both types of applications (regression and classification), Seneca significantly
improves tuning performance over the default and worst case configurations for 
XGBoost and SVC while generating only a slight improvement over default for
Neural Network.

@@

We next analyze the monetary cost effects introduced by Seneca.  To do so, we
use Seneca to find the hyperparameterization that optimizes application output
quality (lowest MSE for regression, highest accuracy for classification).
However note that trying all possible hyperparameterizations incurs a cost.
Further, because Seneca uses AWS Lambda, the amount of memory it uses during
tuning affects this cost.

Thus we compare two Seneca execution configurations.  In the first
we configure each lambda function to
use the maximum amount of memory allowed by AWS Lambda (3008 MB) for all
executions.
Second, we
employ Seneca's memory optimization which automatically detects and configures
the amount of memory needed by each function.  This optimization requires
Seneca to ``probe'' to determine the best memory size to use.  The
cost of these probes
(denoted ``Optimizer Cost'') must be taken intio account as well.
%Because memory impacts both
%cost and execution time (total latency of Seneca hyperparameter tuning), we
%present empirically evaluate both in this subsection.  
Note that XGBoost's performance profile is identical when used for reghression
or classification so we include its measurements only once in the following
analysis.
%For each, we only
%include XGBoost once since its performance profile is the same regardless of
%whether we are using regression or classification.

\begin{table}
\centering
\begin{tabular}{|l|c|c|c|c|c|}
\hline
& Prophet & MR & XGBoost & SVC & NN\\
\hline
\hline
Exec time (minutes)& 24.96 & 4.18 & 17.48 & 0.91 & 2.49 \\
\hline
Seneca Cost (\$) & 0.722 & 0.121 & 0.5 & 0.023 & 0.072 \\
\hline
\end{tabular}
\caption{Monetary cost of using Seneca for hyperparameter tuning when configured to use the maximum amount of memory (3008 MB) possible for each function invocation. 
\label{tab:cost_max_memory}}
%\vspace{-0.2in}
\end{table}

\begin{table}
\centering
\begin{tabular}{|l|c|c|c|c|c|}
\hline
& Prophet & MR & XGBoost & SVC & NN\\
\hline
\hline
Exec time (minutes)& 38.7 & 8.72 & 29.07 & 0.91 & 3.17 \\
\hline
Optimizer Cost (\$) &0.033 & 0.014 & 0.003 & 0.010 & 0.008 \\
\hline
Seneca Cost (\$) &0.62 & 0.086 & 0.354 & 0.007 & 0.056 \\
\hline
Total Cost (\$) &0.653 & 0.1 & 0.357 & 0.016 & 0.064 \\
\hline
\hline
Savings (\$) & 0.07 & \$0.02 & 0.15 & 0.007 & 0.008\\
\hline
Savings (\%) & 10\% & 17\% & 30\% & 30\% & 11\%\\
\hline
\end{tabular}
\caption{Seneca  Memory  Optimization:  The  monetary  cost  of using Seneca for hyperparameter tuning when the amount of memory  used  for  each  function  invocation  is  automatically inferred and set by Seneca.
\label{tab:cost_optimized}}
%\vspace{-0.2in}
\end{table}

Tables~\ref{tab:cost_max_memory} and~\ref{tab:cost_optimized} show the results with and without 
the Seneca memory optimization, respectively. In both tables, the five columns identify the 
benchmark applications and the first row is the total execution time in minutes for 
Seneca's hyperparameter tuning for the corresponding application.  
In Table~\ref{tab:cost_max_memory}, the second row is total cost of tuning when Seneca's 
lambda functions are configured to use the maximum amount of memory (3008 MB). 
Table~\ref{tab:cost_optimized} shows the cost of the memory optimizer in the
second row, Seneca's cost using the optimization in the third row, and total cost on fourth row.
Finally, in the fifth and six rows of Table~\ref{tab:cost_optimized} we show the
savings that memory optimization introduces over using the maximum memory in
dollar cost and as a percentage respectively.

These tables illustrate two important cost features of Seneca.  First, using
AWS Lambda, full hyperparameter space exploration is not expensive in 
\textit{absolute} dollar cost terms.  Even using the maximum memory available
for almost 25 minutes of execution time (cf Prophet in Table~\ref{XXX}), the
total dollar cost is approximately 73 cents.  Secondly, Seneca's memory
optimizations produce a significant percentage savings which, over repeated
executions, is important.

Note also that Seneca's memory/cost optimzation
introduces at an execution time penalty (relative to the maximum memory
execution) for some of the applications.  That is, the
execution times for all applications except SVC increase when Seneca chooses
a memory size.  Thus while Seneca is finding the best application output
quality and optimizing the cost of producing that output, it is doing so at
the expense of execution performance (time to solution).    
The source of this execution performance penalty is not clear.  We hypothesize
that when requesting a large memory for AWS Lambda, Amazon chooses a machine
that also has fast processors so the Lambda functions execute more quickly.
If this supposition is true, then the AWS Lambda pricing model correctly
weights the cost of additional memory (in light of the reduced execution time)
because the large-memory executions are still more expensive.
However regardless of the cause, the Seneca memory optimizer 
provides a way to trade off time to solution for cost when the highest
possible application output quality is desired.
% \textcolor{blue}{See my notes to fix the tables in the caption of these figures.}

@@

%\begin{figure}[t] \centering 
%\includegraphics[scale=0.36]{Cost_analysis_2}
%\caption{The cost analysis of Seneca automatics memory optimization. 
%By reducing the memory use of each, Seneca reduces the monetary cost of hyperparameter tuning by 
%an average of 20\% over using the maximum memory allocatable.\label{fig:cost_analysis}}
%\vspace{-0.2in}
%\end{figure}

%\begin{figure}[t] \centering 
%\includegraphics[scale=0.36]{Latency_analysis_2}
%\caption{Latency of Seneca with (Opt) and without (No Opt) memory optimization, for each application. As Seneca reduces memory use (and cost), it also extends the execution time of the functions (and thus total tuning time, i.e., the latency of Seneca) by Y\% on average across applications \textcolor{blue}{compute and fill in Y here.}
%\textcolor{blue}{Change the legend as follows: change "Optimized Memory" to "Opt"; change "Maximum Memory" to "No Opt"; Make sure that Opt stays green and change No Opt to be red (same as above graph)} 
%\label{fig:latency_analysis}}
%\vspace{-0.2in}
%\end{figure}

%Figure~\ref{fig:cost_analysis} presents the breakdown in the monetary cost of
%using Seneca (performing hyperparameter tuning) with and without its automatic
%memory optimization.  We plot bar graphs for each application across the
%x-axis; the y-axis is monetary cost in US dollars. The stacked column is the
%total cost of tuning by Seneca Memory Optimization, and the green and red
%segments represent the cost of tuning and function optimization respectively.
%The red column at the right-hand side of each application is the total cost of
%tuning by using lambda function at maximum memory. For computation intensive
%applications like Prophet, they generate higher costs, which depend on the
%duration and memory usage on AWS Lambda. %The difference between two costs

%\textcolor{red}{Add analysis here on what the columns are showing -- discuss
%any anomalies (ie why is prophet optimization cost more than the others; why
%mult-regression difference is greater than the others). provide a summary for
%that states the average difference between each pair of bars across
%applications.}
